### 2014-05-21 paper.draft.tex
paper draft

The topology characteristics of the network are also a bit different from the Internet. 
On village-like environments, typical CN deployment may involve a single Access Point 
on the top-roof of the villange from which all the clients contect to. On cities, 
usually the topology is a mesh-like network. Therefore, in both cases the network 
tends to forms clusters of nodes with a very few hops between each other but interconnected 
by long-distance intervilage wireless links.

Locality-aware applications become much important in CN because the cost of leaving 
_your neighberhood cluster_ is particularly expensive since it may involve going 
through several kilometers of unreliable microwave links, with more packet loss, 
more jitter, higher latency and lower throughput.

In this paper, we study the locality of DHT overlay on the context of Community 
Networks. In the next section background on DHT locality is presented.

>>>>

The topology characteristics of the network are also a bit different from the traditional Internet. 
On village-like environments, typical CN deployment may involve a single Access Point 
on the top-roof of the villange from which all the clients contect to. On cities, 
usually the topology is a mesh-like network. Therefore, in both cases the network 
tends to forms clusters of nodes with a very few hops between each other but interconnected 
by long-distance intervilage wireless links.

Locality-aware applications become much important in CN because the cost of leaving 
_your neighberhood cluster_ is particularly expensive since it may involve going 
through several kilometers of unreliable microwave links, with significative packet loss, 
jitter, high latency and low throughput.

In this paper, we study the locality characteristics of DHT overlay on the context of Community 
Networks. In the next section background on DHT locality is presented.
